### 2018-02-23 paper/sections/1_introduction.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

ParSplice molecular dynamics simulations are representative of an important
class of HPC applications with similar working set behaviors that extensively
use software-based caches. It uses a hierarchy of caches and a single
persistent key-value store to store the atomic coordinates corresponding
to local energy minima (referred to simply as minima) encountered
by a large number of independent dynamical trajectories.
This workload is also pervasive
across simulations that (1) rely on a mesh-based decomposition of a physical
region and (2) result in millions or billions of mesh cells, where each cell
contains materials, pressures, temperatures and other characteristics that are
required to accurately simulate phenomena of interest.  The fine-grained data
annotation capabilities provided by key-value storage is a natural match for
these types of scientific simulations.  Unfortunately, simulations of this size
saturate the capacity and bandwidth capabilities of a single node so we need
more effective data management techniques.

>>>>

ParSplice molecular dynamics simulations are representative of an important
class of HPC applications with similar working set behaviors that extensively
use software-based caches. ParSplice uses a hierarchy of caches and a single
persistent key-value store to store the atomic coordinates corresponding
to local energy minima (referred to simply as minima) encountered
by a large number of independent dynamical trajectories.
This workload is also pervasive
across simulations that (1) rely on a mesh-based decomposition of a physical
region and (2) result in millions or billions of mesh cells, where each cell
contains materials, pressures, temperatures and other characteristics that are
required to accurately simulate phenomena of interest.  The fine-grained data
annotation capabilities provided by key-value storage is a natural match for
these types of scientific simulations.  Unfortunately, simulations of this size
saturate the capacity and bandwidth capabilities of a single node so we need
more effective data management techniques.

### 2018-02-23 paper/sections/2_parsplice-keyspace-analysis.tex
paper: typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
    \centering
    \includegraphics[width=1\textwidth]{figures/methodology-keyspace.png}\\
    \caption{Keyspace size and shape.
    \label{fig:methodology-keyspace}}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=0.975\textwidth]{figures/motivation-regimes.png}\\
    \caption{Key accesses over time.
    \label{fig:motivation-regimes}}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=1.05\textwidth]{figures/methodology-keys.png}\\
    \caption{Redundant key accesses.
    \label{fig:methodology-keys}}
  \end{subfigure}
  \caption{Keyspace analysis for ParSplice.
    (a) shows that the keyspace is small but must satisfy many reads. Memory
    usage scales linearly, so we will eventually need more than one node to manage
    segment coordinates for larger jobs. \(\Delta_1\) is the growth rate (see
    Section~\S\ref{sec:delta}).
    (b) shows that key accesses start with many reads to a small set of
    keys and progresses to less reads to a larger set of keys.  The line shows the
    rate that EOM minima values are retrieved from the key-value store (\(y1\));
    points along the bottom show the unique keys accessed in a 1
    second window (\(y2\)). Despite having different
    \(\Delta\)s, the structure of key accesses are similar.
    (c) shows that over time, tasks start accessing a larger set of keys resulting in
    some keys being more popular than others.  Despite different
    \(\Delta\)s, in both runs some keys are \(5\times\) more popular than others.
  }
\end{figure*}

@@

\subsubsection{\underline{Initial conditions influence key activity}}
\label{sec:delta}
Figure~\ref{fig:motivation-regimes} shows how ParSplice tasks read key-value
pairs from the worker's cache for two different initial conditions of
\(\Delta\), which is the rate that new atoms enter the simulation.  The line is
the read request rate (\(y1\) axis) and the dots along the bottom are the
number of unique keys accessed (\(y2\) axis).  The access patterns for
different growth rates have temporal locality, as the reads per second for
\(\Delta_2\) look like the reads per second for \(\Delta_1\) stretched out
along the time axis.  The \(\Delta_1\) growth rate adds atoms every 100K
picoseconds while the \(\Delta_2\) growth rate adds atoms every 1 million
picoseconds. So \(\Delta_2\) has a smaller growth rate resulting in hotter
keys and a smaller keyspace.  Values smaller than \(\Delta_2\)'s growth rate or
a temperature of 400 degrees result in very little database activity because
state transitions take very long. Similarly, growth rate values larger than \(\Delta_1\)'s
lead to far out-of-equilibrium growth, while temperatures in excess of 800 degrees
result in the melting of the nanoparticle, which is not relevant in this application.

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.32\linewidth}
    \centering
    \includegraphics[width=1\textwidth]{figures/methodology-keyspace.png}\\
    \caption{Keyspace size and shape.
    \label{fig:methodology-keyspace}}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=0.975\textwidth]{figures/motivation-regimes.png}\\
    \caption{Key accesses over time.
    \label{fig:motivation-regimes}}
  \end{subfigure}
  \begin{subfigure}[b]{.32\linewidth}
    \includegraphics[width=1.05\textwidth]{figures/methodology-keys.png}\\
    \caption{Redundant key accesses.
    \label{fig:methodology-keys}}
  \end{subfigure}
  \caption{Keyspace analysis for ParSplice.
    (a) shows that the keyspace is small but must satisfy many reads. Memory
    usage scales linearly, so we will eventually need more than one node to manage
    segment coordinates for larger jobs. \(\Delta_1\) is the growth rate (see
    Section~\S\ref{sec:delta}).
    (b) shows that key accesses start with many reads to a small set of
    keys and progresses to less reads to a larger set of keys.  The line shows the
    rate that minima values are retrieved from the key-value store (\(y1\));
    points along the bottom show the unique keys accessed in a 1
    second window (\(y2\)). Despite having different
    \(\Delta\)s, the structure of key accesses are similar.
    (c) shows that over time, tasks start accessing a larger set of keys resulting in
    some keys being more popular than others.  Despite different
    \(\Delta\)s, in both runs some keys are \(5\times\) more popular than others.
  }
\end{figure*}

@@

\subsubsection{\underline{Initial conditions influence key activity}}
\label{sec:delta}
Figure~\ref{fig:motivation-regimes} shows how ParSplice tasks read key-value
pairs from the worker's cache for two different initial conditions of
\(\Delta\), which is the rate that new atoms enter the simulation.  The line is
the read request rate (\(y1\) axis) and the dots along the bottom are the
number of unique keys accessed (\(y2\) axis).  The access patterns for
different growth rates have temporal locality, as the reads per second for
\(\Delta_2\) look like the reads per second for \(\Delta_1\) stretched out
along the time axis.  The \(\Delta_1\) growth rate adds atoms every 100K
picoseconds while the \(\Delta_2\) growth rate adds atoms every 1 million
picoseconds. So \(\Delta_2\) has a smaller growth rate resulting in hotter
keys and a smaller keyspace.  Values smaller than \(\Delta_2\)'s growth rate or
a temperature of 400 degrees result in very little database activity because
state transitions take very long. Similarly, growth rate values larger than \(\Delta_1\)
lead to far out-of-equilibrium growth, while temperatures in excess of 800 degrees
result in the melting of the nanoparticle, which is not relevant in this application.
